---
title: "Aruna_yu_hw7"
output: word_document
---


```{r setup, include=FALSE}

library(rvest)    
library(dplyr)     
library(tidyverse)     
library(repurrrsive)
listviewer::jsonedit(gh_users)  
```

# 1)  Using the following link

```{r}

# Names
Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Movietitles = page%>% html_nodes(".lister-item-header a")%>%
html_text()
Movietitles

# Rating

Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Movieratings = page%>% html_nodes(".ipl-rating-star.small .ipl-rating-star__rating")%>%
html_text()
Movieratings

# Runtime

Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Runtime = page%>% html_nodes(".runtime")%>%
html_text()
Runtime

```

```{r}
Result = data.frame(Movietitles, Movieratings, Runtime)
Result 
```


# 2)
# a) Explain or describe nested Lists.  (Three or four sentences) A nested list is a list that appears as an element in another list. To extract an element from the nested list, we can proceed in two steps. First, extract the nested list, then extract the item of interest. This means the a list in another list.

# b) Open and explore data for Git Hub repos by running the following code gh_repo.  Comment on the structure and arrangement of the data (Two or three sentences) It is nested list, it contains 6 lists in it, 5 of the lists contain 30 items, and one of the list only contains 26 items.

# c)  In two or three sentences, explain what happens to the data when you run the code; After running the code, it is a nested list, it contains 6 lists, but the contents of the lists can not be shown below. So we can use another way to see all the detailed information.

```{r}
 repos <- tibble(repo = gh_repos)
repos
```



# d)  Describe the data representation when the listserver tool is applied. And go into detail explaining why we have a nested List configuration. What do the numbers 30 and 68 represent ? (6 or 7 sentences)Run the following code: We got the nested list because we got the detailed information in this way, all the information are in different levels, we can see different information in different folders, we can't see all the items in one time. When we click into the array[6], we can see 6 items in it. When we continue to click 0[30], it contains 30 items, and also the 68 means the number of the items in it. When we click into 3[26], it contains 26 items in it, and also the 68 represents the number of items in it.

```{r}
listviewer::jsonedit(gh_repos)
```

# e)  Use and show R unesting code to produce the tibble below.

```{r}
# (users <- tibble(user = gh_users))
# 
# # Lets take a look at the list data for each Github user
# 
# listviewer::jsonedit(gh_users)
# 
# # Now use the following code to print out the same information
# # in the console
# 
# names(users$user[[1]])
# 
# # Now transform the nested data into a data frames
# 
# users %>%
#   unnest_wider(user)
# # Note that the characteristics have become column variables
# repos <- tibble(repo = gh_repos)
# repos
# listviewer::jsonedit(gh_repos)
#class(users)
# You may not want all of the column variables.  You can use the command
# hoist to select the variables and list content that you want.
# users %>% hoist(user,
#                id = "is",
#                name = "name",
#                full_name = "full_name",
#                owner = "owner",
#                private = "private",
#                html_url = "html_url",
#                description = "descriation",
#                fork = "fork",
#                url = "url") -> u
tibble(repo = gh_repos) %>%
  unnest_auto(repo) %>%
  unnest_auto(repo)

```


